The Next Release Problem in Real World

### 2018-12-15 PaperBody.tex
ILP, result, graphs added

\subsection{Type Changes and {\itshape Special} Characters}

@@

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

>>>>

\section{Algorithms}
\subsection{Analytic Hierarchy Process(AHP)}
\subsection{Integer Linear Programming(ILP)}
Integer Linear Programming(ILP) is optimization method whose objective function and constraints are linear, and all variables are integer. We referred ILP at the paper \textit{<An Integer Linear Programming approach to the single and bi-objective Next Release Problem>} by N Veerapen et al. This paper used ILP solver named \textit{CPLEX}, but it is commercial solver so we used \textit{PuLP}(modeler) and \textit{Gurobi}(solver) for this project. \textit{PuLP} is free open source software so users can use it by pip install. However general \textit{Gurobi} solver is commercial one so we registered to \textit{Gurobi (www.gurobi.com)} and used \textit{Gurobi} academic version. \\
\subsection{Simulated Annealing(SA)}
\subsection{Genetic Algorithm(GA)}
\subsection{NSGA-II}

\begin{table*}
  \caption{Profit Comparison}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    &eclipse-log&firefox-log&firefox-priority&firefox-comments+priority\\
    \midrule
    Real Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
    Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
    \hline
    SA&3702.85182&13524.93411&16300.0&28358.2295685 \\
    GA&3793.5045&13662.38600&16303.0&28522.11861 \\
    NSGA-II&3822.47741&13700.52067&16518.33333&28729.33476 \\
    ILP&3825.42768&13768.44722&16336.0&28845.23124 \\
    AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
    \bottomrule
  \end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\begin{figure*}[h]
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_eclipse_log(comments)_2016meancost.JPG}
\caption{bugzilla-eclipse-log(comments)-2016meancost}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
\caption{bugzilla-firefox-log(comments)-2016meancost}
\label{fig:subim2}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_priority_2016meancost.JPG}
\caption{bugzilla-firefox-priority-2016meancost}
\label{fig:subim3}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_comments-priority_2016meancost.JPG}
\caption{bugzilla-firefox-comments+priority-2016meancost}
\label{fig:subim4}
\end{subfigure}

\caption{Profit Comparison for each dataset}
\label{fig:image1}
\end{figure*}

\begin{figure*}[h]
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{SA-correlation.JPG}
\caption{SA}
\label{fig:subim5}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{GA-correlation.JPG}
\caption{GA}
\label{fig:subim6}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{ILP-correlation.JPG}
\caption{ILP}
\label{fig:subim7}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{AHP-correlation.JPG}
\caption{AHP}
\label{fig:subim8}
\end{subfigure}

\caption{Cost-Profit Correlation}
\label{fig:image2}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=0.9\linewidth]{cost-profit-together.JPG}
\caption{Cost-Profit Correlation in one graph}
\label{fig:image3}
\end{figure*}

\section{result}
At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other. In \textbf{table 1}, upper two rows are real cost sum and real profit sum of each datasets. Below these rows, there are maximum profits for each algorithms in four datasets. At the result, every maximum profits are bigger than real profit sum. Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II. \\
\textbf{Figure 1} is the graphs of \textbf{table 1}. Each graph expresses the maximum profit of five algorithms. At the result, the maximum profit of ILP is the biggest, and the maximum profit of NSGA-II and AHP is bigger than the maximum profit of SA and GA in most case. Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA. Peculiar thing is that, in dataset \textit{bugzilla-firefox-priority-2016meancost}, NSGA-II is largely bigger than other four algorithms. The reason we suppose is that other three datasets' profit is variety because the number of comments is not bounded, but this dataset's profit is priority, which is varied only in 1, 2, 3, 4, and 5 points. In this case, requirements can be seen more similar each other than other datasets. This difference could influence the difference of the result.\\
At experiment 2, we applied four algorithms except NSGA-II to dataset \textit{bugzilla-firefox-comments+priority-2016meancost}. At this experiment, we got the maximum profits while changing the cost constraints. The result is expressed in \textbf{Figure 2} and \textbf{Figure 3}. \textbf{Figure 2} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms. \\
The result is that they are all increasing almost linearly and similarly. One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.
\subsection{Type Changes and {\itshape Special} Characters}

@@
